Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-01-30 src/tex/ms.tex

\subsection{Result on GWTC-3}
% Violin plot
In figure \ref{fig:violin_kappa}, we show the posterior of $\kappa$ for each event in the form of a violin plot.
The median and confidence interval of $\kappa$ are calculated with the restricted posterior distribution of $\kappa$, which is given by equation \ref{eq:restricted_posterior}.
We excluded GW200129 from the calculation of the median and confidence interval of $\kappa$.
Details of the exclusion are discussed in Sec.~\ref{sec:GW200129}.

\begin{figure*}[ht]
    \script{violin_kappa.py}
    \includegraphics[width=\textwidth]{figures/violin_kappa.pdf}
    \caption{
        The violin plot shows the posterior of $\kappa$ for 69 events in this study.
        Each violin represents a different event.
        The color of the violins represents the quotient of the median and standard deviation of the posterior.
        The blue horizontal solid line represents the median of the restricted posterior of $\kappa$, and the blue dashed lines enclose the $90\%$ confidence interval of the restricted posterior of $\kappa$.
        The pink horizontal solid line represents $\kappa=0$.
    }
    \label{fig:violin_kappa}
\end{figure*}

>>>>

\subsection{Result on GWTC-3}
% Violin plot
In figure \ref{fig:violin_kappa}, we show the posterior of $\kappa$ for each event in the form of a violin plot.
The median and confidence interval of $\kappa$ are calculated with the restricted posterior distribution of $\kappa$, which is given by equation \ref{eq:restricted_posterior}.
We excluded GW200129 from the calculation of the median and confidence interval of $\kappa$ in figure \ref{fig:violin_kappa}.
Details of the exclusion are discussed in Sec.~\ref{sec:GW200129}.

\begin{figure*}[ht]
    \script{violin_kappa.py}
    \includegraphics[width=\textwidth]{figures/violin_kappa.pdf}
    \caption{
        The violin plot shows the posterior of $\kappa$ for 70 events in this study.
        Each violin represents a different event.
        The color of the violins represents the quotient of the median and standard deviation of the posterior.
        The blue horizontal solid line represents the median of the restricted posterior of $\kappa$, and the blue dashed lines enclose the $90\%$ confidence interval of the restricted posterior of $\kappa$.
        The pink horizontal solid line represents $\kappa=0$.
    }
    \label{fig:violin_kappa}
\end{figure*}
